PAGAI : a path sensitive static analyser

### 2012-05-16 papers/TAPAS2012/pagai.tex
TAPAS

\newcommand{\Nat}{{\mathbb N}}
\newcommand{\Real}{{\mathbb R}}
\def\lastname{Henry}
\begin{document}
\begin{frontmatter}
  \title{PAGAI} 
  \author{Julien Henry \thanksref{imag.fr}}
  \address{Universit\'e Joseph Fourier, VERIMAG\\
    Grenoble, France} 
	\author{David Monniaux\thanksref{imag.fr}}
  \address{CNRS, VERIMAG\\
    Grenoble, France} 
	\author{Matthieu Moy\thanksref{grenoble-inp.fr}}
  \address{Grenoble-INP, VERIMAG\\
    Grenoble, France}

    \thanks[imag.fr]{Email:
    \href{First Name.Last Name@imag.fr} {\texttt{\normalshape
        First Name.Last Name@imag.fr}}} 
    \thanks[grenoble-inp.fr]{Email:
    \href{Matthieu.Moy@grenoble-inp.fr} {\texttt{\normalshape
        Matthieu.Moy@grenoble-inp.fr}}} 
\begin{abstract} 
	We present design and implementation of PAGAI, a new static analyzer 
	working over the LLVM compiler infrastructure, that computes inductive
	invariants on the numerical variables of the program.
	PAGAI implements various state-of-the-art techniques combining Abstract
	Interpretation and Decision Procedures (SMT-solving), and offers
	several abstract domains.
	We thus can compare in time and precision the various combinations of
	techniques and abstract domains. We conducted extensive experiments for
	comparing these techniques on several benchmarks and GNU programs.
\end{abstract}
\begin{keyword}
	Static Analysis, Program Verification, Abstract Interpretation, Decision
	Procedure, Satisfiability Modulo Theories.
\end{keyword}
\end{frontmatter}
\section{Introduction}\label{intro}
Static analysis aims at automatically computing properties on programs, such as
the possible values of their variables during execution. This allows to show for
instance that a program has no runtime error (such as arithmetic overflow,
division by zero), to compute loop invariants, etc. The main applications of
static analysis are compile-time optimisations, and the proof of safety
properties in critical systems.
Abstract Interpretation is a general framework for fully automatic static
analysis, that computes inductive invariants at various control points of an
imperative program. Linear Relation Analysis (LRA) is a direct application of
this framework, that computes an upper-approximation of the set of the reachable
states of a numerical program.

@@

These techniques make a precise analysis of the paths inside the program

>>>>

\newcommand{\Nat}{{\mathbb N}}
\newcommand{\Real}{{\mathbb R}}
\def\lastname{Henry}
\begin{document}
\begin{frontmatter}
  \title{PAGAI : a path sensitive static analyser} 
  \author{Julien Henry \thanksref{imag.fr}}
  \address{Universit\'e Joseph Fourier, VERIMAG\\
    Grenoble, France} 
	\author{David Monniaux\thanksref{imag.fr}}
  \address{CNRS, VERIMAG\\
    Grenoble, France} 
	\author{Matthieu Moy\thanksref{grenoble-inp.fr}}
  \address{Grenoble-INP, VERIMAG\\
    Grenoble, France}

    \thanks[imag.fr]{Email:
    \href{First Name.Last Name@imag.fr} {\texttt{\normalshape
        First Name.Last Name@imag.fr}}} 
    \thanks[grenoble-inp.fr]{Email:
    \href{Matthieu.Moy@grenoble-inp.fr} {\texttt{\normalshape
        Matthieu.Moy@grenoble-inp.fr}}} 
\begin{abstract} 
	We present design and implementation of PAGAI, a new static analyzer 
	working over the LLVM compiler infrastructure, that computes inductive
	invariants on the numerical variables of the program.
	PAGAI implements various state-of-the-art techniques combining Abstract
	Interpretation and Decision Procedures (SMT-solving), that allow to do a
	precise analysis of the various paths in a program.
	We thus can compare in time and precision the various combinations of
	techniques and abstract domains. We conducted extensive experiments for
	comparing these techniques on several benchmarks and GNU programs.
\end{abstract}
\begin{keyword}
	Static Analysis, Program Verification, Abstract Interpretation, Decision
	Procedure, Satisfiability Modulo Theories.
\end{keyword}
\end{frontmatter}
\section{Introduction}\label{intro}
Static analysis aims at automatically computing properties on programs, such as
the possible values of their variables during execution. This allows to show for
instance that a program has no runtime error (such as arithmetic overflow,
division by zero), to compute loop invariants, etc. The main applications of
static analysis are compile-time optimisations, and the proof of safety
properties in critical systems.
Abstract Interpretation is a general framework for fully automatic static
analysis, that computes inductive invariants at various control points of an
imperative program. Linear Relation Analysis (LRA) is a direct application of
this framework, that computes an upper-approximation of the set of the reachable
states of a numerical program.

@@

Exemple du boustrophedon ???
These techniques make a precise analysis of the paths inside the program
